%Chapter of Introductions
%Pretty self explanatory really

\chapter{Introduction}
\label{intro}

%----------------------------------------------------------------------------------------

% Define some commands to keep the formatting separated from the content 
\newcommand{\keyword}[1]{\textbf{#1}}
\newcommand{\tabhead}[1]{\textbf{#1}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\file}[1]{\texttt{\bfseries#1}}
\newcommand{\option}[1]{\texttt{\itshape#1}}

%----------------------------------------------------------------------------------------

The Internet of Things or IoT is the concept of a huge network of physical objects connected together and communicating between themselves and to the world wide web. Devices can include domestic appliances, cars and even buildings. It is a rapidly growing field with over 50 million devices expected to be connected to the web by 2020\cite{50milby2020}. As such the security of the transmissions of these devices is becoming a more and more pressing issue. IoT's main benefits are the remote control of devices and appliances, the ability of the device to send information about it's state, such as a vending machine reporting that it has run out of a certain item, and to allow the machines to be more automated and to work with other machines, like a home hub device that can turn on the lights and central heating when an occupant is arriving home, with the lights and heating not being connected to each other but to the central hub.
	
	However IoT benefits will be severely limited if it unsecure. IoT is an emerging field but there have already been some high profile security disasters. Ranging from relatively less serious problems such as some attackers being able to glean WiFi network information from internet connected lights\cite{hackingsum} to the very concerning and potentially fatal security breaches like someone gaining unauthorised access to your car and assuming control. There have been three examples of this in the last few years with a Jeep Cherokee\cite{jeephack}, a Toyota Prius\cite{priushack} and a Tesla Model S\cite{teslahack} being the cars effected. The hackers were able to control the accelerator, door locks and brakes, among other things. In the Jeep Cherokee the attackers remotely disabled the engine of the car as it was driving up a freeway at 70 MPH. This highlights a very real problem that will only become more important as the field grows. Too often security is an afterthought but it really needs to be built into products from the offset.

	The challenge is to provide a cryptographic solution that is similar in strength of security to solutions that are implemented on more powerful servers and computers but on much smaller and less powerful devices. A solution that performs at an acceptable speed and provides good security with reduced power consumption.
	
	Google and British Gas have recently released Nest and Hive respectively. Nest was released in 2014 and Hive in 2013. These both involve controlling your central heating remotely and programming in days when you won't be at home and therefore have no need of heating. However, it was two whole years later upon independent investigators discovering that information, such as the dates when the heating was on or off, was being sent unencrypted that British Gas decided to encrypt their product Hive's transmissions. This plaintext data could be used to work out when the occupants were away as the central heating was likely to be off in that case. With the release of Hive 2 they patched the problems found but they should never have been there in the first place. Found in the same investigation, Google had a lesser fault with Nest which was sending the post code of the user unencrypted, which has since been patched. It is only when caught or there is a high profile breach that companies take the steps to fully secure their customers information \cite{which}. 
	
	Security on IoT devices is a new implementation of an old problem, developers and companies sometimes don't employ effective security on the private data they store, moving to smaller internet connected devices doesn't change this fundamental problem. There are studies about and examples of cryptographic systems for microcontrollers, it is not something that cannot be done. However, perhaps it is too difficult at present for smaller development teams or has too much of a foot print in terms of computational resources, power or time that it gets pushed to the side. Data security is a fundamentally important concept and one that is necessary for the implementation of all applications, especially those that involve user's private data otherwise there is the potential for loss of money, intellectual property, goods, reputation and health. These problems affect both companies and the consumer.
	
	This project will look into creating a solution for the transmission of secure, authenticated and encrypted data across an unsecure network that can be easily implemented, has a small code size and acceptable performance and security considering the code is run on a low powered device. As it is low powered the power consumption will be monitored as that would be a consideration if the device was to be powered by batteries. The example used to work with is the secure transmission of a user's private temperature data. If they have a system that monitors the temperature of rooms, that data can be used to figure out when they are likely to be home or not. So, using a base platform in the user network that has access to the temperature sensors throughout the house, it takes the sensor data, signs then authenticate encrypts it before sending it to a remote server. 
	
	
	